correlation_part2

### 2022-05-19 graphs_newt_snakes/correlation_part2.Rmd
Peter and I talked about the per unit caculations and found an error in the correlations

GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==29981 ),]

@@

@@

  plot <- ggplot(var_cor_table) +
  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  #xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

>>>>

GA1_onefile<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-10_0.5_Snake_1.0e-10_0.5_0" & data_long_max$gen==10981 ),]

@@

unique(data_long_mean$newt_snake_rep)

GA1_onefile_2<-data_long_mean[which(data_long_mean$newt_snake_rep=="Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0" & data_long_max$gen==10981 ),]

ggplot(GA1_onefile_2)+

  geom_point(data = GA1_onefile_2[which(GA1_onefile_2$species=="snake"),], aes(x = lox, y = loy, fill = measurement), size = 10, shape = 22, ) +
  geom_point(data = GA1_onefile_2[which(GA1_onefile_2$species=="newt"),], aes(x = lox, y = loy, fill = measurement), size = 7, shape = 21, ) +
  scale_fill_viridis_c()+
  theme_bw()

```{r pheno scatter}

snake_info<-data_long_mean[which(data_long_mean$species=="snake"),]
newt_info<-data_long_mean[which(data_long_mean$species=="newt"),]

names(newt_info)[names(newt_info) == 'measurement'] <- 'newt_toxin'
newt_info$snake_res<-snake_info$measurement
newt_info$dif<-newt_info$snake_res-newt_info$newt_toxin
pattern<-"Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0"
scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation>14000 & newt_info$generation<15000 ),]
scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
#scatter_pheno[scatter_pheno == 0] <- NA
#scatter_pheno[scatter_pheno == 1] <- NA
ggplot(scatter_pheno)+
 ggtitle(paste0(" pattern ", pattern, " From ", min(scatter_pheno$generation), " gen to ", max(scatter_pheno$generation), " gen"))+
  geom_point(aes(y = newt_toxin, x = snake_res, color=generation), size = 3) 
  theme_bw()

@@

  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
